Predicting _C. difficile_ Infection Severity from the Taxonomic Composition of the Gut Microbiome

### 2023-06-01 paper/paper.qmd

```{r sample_counts}
#| label: tbl-counts
#| tbl-pos: h
#| tbl-cap: "**Sample counts and proportion of severe cases.** Each severity 
#|   definition has a different number of patient samples available, as well as
#|   a different proportion of cases labelled as severe.
#| "
#| tbl-subcap: 
#|   - "Full datasets"
#|   - "Intersection of samples with all labels available"
#| layout-ncol: 2
format_table <- function(tab) {
  tab %>%
    kable(col.names = c(' ', 'IDSA', 'Attributable', 'All-cause', "Pragmatic"),
          format.args = list(big.mark = ',')) %>% 
    kable_styling(font_size = table_font_size)
}
read_csv(here('results','count_table_full.csv')) %>% 
  format_table()
read_csv(here('results','count_table_int.csv')) %>% 
  format_table()
```

>>>>

```{r sample_counts}
#| label: tbl-counts
#| tbl-pos: h
#| tbl-cap: "**Sample counts and proportion of severe cases.** Each severity 
#|   definition has a different number of patient samples available, as well as
#|   a different proportion of cases labelled as severe.
#| "
#| tbl-subcap: 
#|   - "Full datasets"
#|   - "Intersection of samples with all labels available"
#| layout-ncol: 2
format_table <- function(tab) {
  tab %>%
    kable(col.names = c(' ', 'IDSA', 'All-cause', 'Attributable', "Pragmatic"),
          format.args = list(big.mark = ',')) %>% 
    kable_styling(font_size = table_font_size)
}
read_csv(here('results','count_table_full.csv')) %>% 
  format_table()
read_csv(here('results','count_table_int.csv')) %>% 
  format_table()
```
